An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-25 paper/paper.tex

Note the emphasis of the action taken by each: a peer is said to \textit{back up} data, and a node is said to \textit{store} a replica of the peer's data.

PeerStore showed that separating the metadata layer from the data layer can result in significant bandwidth reduction. By relaxing the requirement to strictly maintain a set number of replicas per file, the system can reduce the data migration cost. For example, it is unnecessary to \textit{immediately} find a new replication node when a current replication node goes offline; only when the node has shown to be consistently unavailable should the system seek a replacement. Given that there exists more than one replica of a peer's data, having one temporarily offline is not catastrophic.\footnote{Note that this implies the low possibility of not being able to recover data that is backed up. Also note that this situation is unavoidable in \textbf{all} backup systems. We leverage this fact by relaxing the aforementioned requirement like PeerStore; this sacrifices theoretical availability for performance and usability. See Section \ref{subsec:TheMetadataLayer_sec:SystemDesign} for the discussion of the parameterization of these variables in our implementation. See Section \ref{} for our methodology of testing the parameter. Finally, see Section \ref{} for a comparison of the results of different values for the parameter.}
%  add references once we know section names

>>>>

Note the emphasis of the action taken by each: a peer is said to \textit{back up} data, and a node is said to \textit{store} a replica of the peer's data. Understanding this distinction will aid in understanding the description of our system.

PeerStore showed that separating the metadata layer from the data layer can result in significant bandwidth reduction. By relaxing the requirement to strictly maintain a set number of replicas per file, the system can reduce the data migration cost. For example, it is unnecessary to \textit{immediately} find a new replication node when a current replication node goes offline; only when the node has shown to be consistently unavailable should the system seek a replacement. Given that there exists more than one replica of a peer's data, having one temporarily offline is not catastrophic.\footnote{Note that this implies the low possibility of not being able to recover data that is backed up. Also note that this situation is unavoidable in \textbf{all} backup systems. We leverage this fact by relaxing the aforementioned requirement like PeerStore; this sacrifices theoretical availability for performance and usability.}
